Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-08-24 stp/paper_aaai/main.tex
one last comment
added citeasnoun command to remove parenthesis of citations

@@

\end{tikzpicture}
\caption{Example of ontology
(`\tikz{ \node[class] () at (0,0)  {};}' are Classes, `\tikz{ \path[hasaC,->] 
(0,1) -- (3ex,1);}' means ``has a Class property'', 
`\tikz{ \path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
means ``has 
a data 
property'' and 
`\tikz{ \path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ). Based on 
\cite{Taheriyan2013}.
}
\label{FIG:onto}
\end{figure}

@@

Note that we keep all the matches, regardless of the confidence of the match. 
This is an important difference between our system and other approaches 
\cite{taheriyan2016learning} that 
remove some of the matches based on heuristics in order to simplify the task of 
finding the semantic model.

@@

The majority of approaches to solve the \relonto{} mapping problem are based on 
heuristic rules and alignment of constraints specified within relational 
schemata and ontologies.
A very comprehensive overview and comparison of existing mapping generation tools based on this approach is given in~\cite{Pinkel:rodi} and~\cite{Spanos:semweb}.
As examples, there are BootOX~\cite{Jimenez:Bootox}, MIRROR~\cite{Luciano:Mirror} and  ontop~\cite{Fagin:Clio}.
Crudely speaking, these tools first apply a default direct mapping specified by the W3C.
Further, the default ontology is enriched by using explicit and implicit schema constraints.
Finally, ontology alignment techniques are applied to match the default ontology to the target ontology.
The main advantage of these systems is the ability to run in a fully automatic setting.
Our approach is complementary to the approaches from this group and at its current stage is semi-automatic.
However, constraint programming offers a convenient framework to incorporate integrity constraints specified either within relational or ontological schema as additional constraints to govern the search for the solution.
This opens an interesting direction for further research to develop an automatic system.

A major issue with fully automatic systems is that constraints may be 
inconsistent or absent completely, e.g., data from Web services or tables on 
the Web.
To overcome this issue, we can apply ML techniques.
\cite{Limaye:Annotating} design a system to annotate web tables with entities for cell values, semantic labels for attributes and relationships for binary combinations of attributes.
As in our approach, they decompose the process of mapping into two main stages: semantic labeling and finding relationships between matched semantic labels.
\cite{Limaye:Annotating} enrich their data sources by using YAGO.
\cite{Mulwad:Semantic} extend this approach by leveraging information from Wikitology Knowledge Base (KB).
\cite{Venetis:Recovering} develop a scalable approach to recover the semantics of Web tables by incorporating data from the isA database KB.
\cite{Ritze:matching}, on the other hand, use DBPedia as their KB.
%extract additional data from knowledge bases to assign a semantic label to an attribute.
Hence, these approaches are limited to domains well represented in those knowledge bases.
Also, they are not able to find the relation between attributes in the table if there is no direct connection between the attributes.
Our approach, on the other hand, allows a model to be trained on any data and can infer complex semantic paths which might exist between attributes.
However, it might be further bootstrapped by leveraging external knowledge bases.
This is especially beneficial at the start when the system does not have sufficient training data.

@@

We build upon the work of~\cite{taheriyan2016learning} and use their ideas for the construction of the alignment graph.
The only difference is that we introduce the \emph{unknown} and \emph{root} class nodes and as many \emph{unknown} data nodes as there are attributes in the modeled data source.
These nodes serve to capture the unmatched attributes from the source.
Though we have modified \karma{} to treat these additional nodes as well, our 
approach outperforms \karma{} since we have additional constraints for these 
nodes and use an exact algorithm to solve the STP.
\cite{taheriyan2016learning} treat the matching and STP parts of \relonto{} independently and use heuristic algorithms for both.
We, on the other hand, use exact algorithms for both parts and address them within a unified CP model.

>>>>

\newcommand{\citeasnoun}[1]{\citeauthor{#1}~\shortcite{#1}}

@@

\end{tikzpicture}
\caption{Example of ontology
(`\tikz{ \node[class] () at (0,0)  {};}' are Classes, `\tikz{ \path[hasaC,->] 
(0,1) -- (3ex,1);}' means ``has an object property'', 
`\tikz{ \path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
means ``has a data property'' and 
`\tikz{ \path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ). Example by
\citeasnoun{Taheriyan2013}.
}
\label{FIG:onto}
\end{figure}

@@

Note that we keep all the matches, regardless of the confidence of the match. 
This is an important difference between our system and other approaches 
\cite{taheriyan2016learning} that 
remove some of the matches based on heuristics in order to simplify the task of 
finding the semantic model. \ddg{is this last paragraph true?}

@@

The majority of approaches to solve the \relonto{} mapping problem are based on 
heuristic rules and alignment of constraints specified within relational 
schemata and ontologies.
A very comprehensive overview and comparison of existing mapping generation 
tools based on this approach is given by~\citeasnoun{Pinkel:rodi}
and~\citeasnoun{Spanos:semweb}.
As examples, there are BootOX~\cite{Jimenez:Bootox}, MIRROR~\cite{Luciano:Mirror} and  ontop~\cite{Fagin:Clio}.
Crudely speaking, these tools first apply a default direct mapping specified by the W3C.
Further, the default ontology is enriched by using explicit and implicit schema constraints.
Finally, ontology alignment techniques are applied to match the default ontology to the target ontology.
The main advantage of these systems is the ability to run in a fully automatic setting.
Our approach is complementary to the approaches from this group and at its current stage is semi-automatic.
However, constraint programming offers a convenient framework to incorporate integrity constraints specified either within relational or ontological schema as additional constraints to govern the search for the solution.
This opens an interesting direction for further research to develop an automatic system.

A major issue with fully automatic systems is that constraints may be 
inconsistent or absent completely, e.g., data from Web services or tables on 
the Web.
To overcome this issue, we can apply ML techniques.
\citeasnoun{Limaye:Annotating} design a system to annotate web tables with 
entities for cell values, semantic labels for attributes and relationships for 
binary combinations of attributes.
As in our approach, they decompose the process of mapping into two main stages: semantic labeling and finding relationships between matched semantic labels.
\citeasnoun{Limaye:Annotating} enrich their data sources by using YAGO.
\citeasnoun{Mulwad:Semantic} extend this approach by leveraging information 
from Wikitology Knowledge Base (KB).
\citeasnoun{Venetis:Recovering} develop a scalable approach to recover the 
semantics of Web tables by incorporating data from the isA database KB.
\citeasnoun{Ritze:matching}, on the other hand, use DBPedia as their KB.
%extract additional data from knowledge bases to assign a semantic label to an attribute.
Hence, these approaches are limited to domains well represented in those knowledge bases.
Also, they are not able to find the relation between attributes in the table if there is no direct connection between the attributes.
Our approach, on the other hand, allows a model to be trained on any data and can infer complex semantic paths which might exist between attributes.
However, it might be further bootstrapped by leveraging external knowledge bases.
This is especially beneficial at the start when the system does not have sufficient training data.

@@

We build upon the work of \citeasnoun{taheriyan2016learning} and use their 
ideas for the construction of the alignment graph.
The only difference is that we introduce the \emph{unknown} and \emph{root} class nodes and as many \emph{unknown} data nodes as there are attributes in the modeled data source.
These nodes serve to capture the unmatched attributes from the source.
Though we have modified \karma{} to treat these additional nodes as well, our 
approach outperforms \karma{} since we have additional constraints for these 
nodes and use an exact algorithm to solve the STP.
\cite{taheriyan2016learning} treat the matching and STP parts of \relonto{} independently and use heuristic algorithms for both.
We, on the other hand, use exact algorithms for both parts and address them within a unified CP model.
